\huge A Usability Evaluation of Tor Launcher

### 2016-11-11 pets2017-paper/pets2017-paper.tex
changes from David's feedback

Tor minimizes collecting user data. Therefore, Tor does not have data on how users interact with the configuration interface. While we agree that this is respectful to the users, we also believe that this data will be helpful to improve the usability of the configuration interface. Improving the usability of the configuration interface has the obvious benefit of helping more users connect to Tor. But this is also benefits the Tor company (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).

@@

Tor relays are routers in the Tor Network that receive and route Tor traffic. 
The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays which direct traffic to the destination.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
\caption{
Bridge options in Tor Browser~5.0.3's Tor Launcher interface.
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
%Under ``Enter custom bridges,'' there is a space to paste in
%a bridge line, obtained out of band.
%The ``Help'' button displays instructions on obtaining
%bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

@@

@@

\subsection{State and Corporate Censorship}
State level censors block access to the Tor network by blocking Tor relays, which are publicly listed. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect to the Internet, but not through Tor. The thoroughness of censorship is what requires different bridges and transports.

\subsection{Connecting to Tor} 
Configuring a bridge requires providing one or more
``bridge lines,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

@@

\begin{itemize}
\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
\end{itemize}

@@

We used Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3). 
We used the Windows operating system hosts file to to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). We blocked torproject.org and its subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers.  We blocked wikipedia.org, cnn.com, and their subdomains to create ``censored'' sites for the experiment.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
	\label{fig:old-bridge}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\caption{Instructions on getting a custom bridge.Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
	\label{fig:old-proxy}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\caption{Where users fill in proxy information.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\caption{The progress bar.}
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

@@

More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies. We doubted that users would have an understanding of how the Internet well enough to even explain how Tor relays, bridges, and proxies worked. Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing. The notion of bridges and transports are also specific to Tor, and not other censorship circumvention software.

@@

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started the recording the computer screen.

@@

The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}). This purpose of this introduction was to ensure that the main task
was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
We instructed them to visit a blocked and unblocked website
in a non-Tor browser to clarify that the Internet was functioning as expected. 
We then told them to use Tor Browser to visit a censored site and pointed out 
the respective shortcut on their desktop.

@@

In E1, any connection to Tor worked. Configuring bridges and proxies were optional.  
Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges. 
Observations in E1:

@@

%P12 (regular): E2 (10:40; 0:46 to 11:26)
\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly. They then looked at proxy settings, gave up, and tried connecting directly again. Then, they tried to configure a proxy, and gave up. They tried a direct connection again, which worked. E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instructions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

@@

\noindent To minimize work: 
\begin{itemize}
\item We eliminated technical questions, resulting in less tasks and interface screens. 
\item We simulated auto-detection for proxies, telling users that they did not need a proxy. This is feasible to do with a local scan (no information leaked). 
\item We labeled the configure button as an option for users in heavily censored environments.
\item We gave advice on choosing transports, telling users to try a meek bridge if obfs3 does not work.
\end{itemize}

@@

Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and start the video recording. In contrast to the previous test, we installed an instrumented versions of Tor Browser 5.0.3. The instrumentation logged user interactions, such as window transitions, mouse clicks, and menu selections. Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment. Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.

@@

\begin{table}[t]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
& \multicolumn{2}{r}{(at 40 minutes)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

%table
\begin{table}[t]
\centering
\input{attempts-bridge-proxy.tex}
\caption{
Network components that led to the first successful bootstrap
in each condition.
Most successful E1 participants used a direct connection,
but a few optionally used an obfs3 bridge.
All successful E2 participants used 
an obfs3 bridge (the recommended option)---none used 
flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
Most successful E3 participants
used a meek bridges, disfavoring meek-azure.
One E3 participant succeeded in an unexpected way
by using an open proxy and configuring it to bypass our 
simulated environment.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
Cumulative success rates over time, shown continuously and at discrete times we found interesting.
For the purposes of plotting the cumulative distribution, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes. 
Notice that the longer the time went on, participants were less likely to succeed. 
At 1.5 minutes, every E1-NEW participant finished,
but only 58\% of E1-OLD had finished by that time.  
At 10 minutes, most participants in E2 had finished. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

%things to keep in mind
We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1, and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again. But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.

%configuration time and version
Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$). That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of configuration times were also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.

\begin{table}[t]
\centering
\input{median_time.tex}
\caption{The median percent of time spent on each screen, which is not
necessarily the median absolute time spent on that screen. 
This percentage is computed independently for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.} 
\label{table:median_time}
\end{table}

@@

\begin{itemize}
\item {\bfseries Hide infrequent options.} Hide the proxy configuration screen and less-used transports. None of our participants connected using flashproxy, fte, fte-ipv6, or scramblesuit transport bridges. 
\item {\bfseries Give advice.} Discourage users from configuring optional components. Add a secondary recommendation for bridges (try meek if obfs3 doesn't work, use meek if you are in Syria) to help users in need. 
\item {\bfseries Minimize work.} Detect if users need a proxy or not. Redirect users to the relevant pages on error (i.e. redirect to the bridge screen the bridge fails).  
\item {\bfseries Provide feedback.} Tell users what to do when a specific error occurs (i.e. try the same connection again, pick another bridge, try without a proxy, etc.).  Show users their bridge and proxy settings before and during connection. Fix the progress bar so that it updates on subsequent connections.
\end{itemize}

@@

\section{Limitations}
\label{sec:limitations}
We did not study international users, or the configuration interface in languages other than English. All of our participants were from the United States and instructed to interact with the English version of Tor Browser.

Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}. We are aware that our participants were likely motivated differently compared to real users. We believe that participants were likely overmotivated to connect to Tor because they were being observed and receiving a monetary reward. If true, this makes our results are a conservative estimate of the current usability problems.

@@

Our experiment did not directly test more advanced tasks. Our simulated environments did not require users to configuring a proxy or to get a custom bridge. From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how much they do.

We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent. Additionally, we acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.

@@

\section{Conclusion} 
\label{sec:conclusion}
The Tor Launcher GUI allows most users to connect to the Tor network, provided that the user's connection does not require a proxy or a non-default bridge. User observation showed that participants were intimidated of the tasks, unsure of what to do, and likely to get stuck configuring proxies that they did not need. User testing showed that most people take more than 10 minutes to connect to Tor if they need to use bridges.

>>>>

Tor minimizes collecting user data. Therefore, Tor does not have data on how users interact with the configuration interface. While we agree that this is respectful to the users, we also believe that this data will be helpful to improve the usability of the configuration interface. Improving the usability of the configuration interface has the obvious benefit of helping more users connect to Tor. But this is also benefits the Tor Project (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).

@@

Tor relays are routers in the Tor Network that receive and route Tor traffic. 
The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays that direct traffic to the destination.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.

@@

\subsection{State and Corporate Censorship}
State level censors block access to the Tor network by blocking Tor relays, which are publicly listed. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect directly to websites, but some may be blocked as is Tor. The thoroughness of censorship is what requires different bridges and transports.

@@

\subsection{Connecting to Tor} 
Configuring a bridge requires providing a
``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata.
The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

@@

\begin{itemize}
\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, not counting time spent passively waiting.
\end{itemize}

@@

We used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
We used the Windows operating system hosts file to to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). We blocked torproject.org and its subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers.  We blocked wikipedia.org, cnn.com, and their subdomains to create ``censored'' sites for the experiment.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\caption{Instructions on getting a custom bridge. Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\caption{Where users fill in proxy information.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\caption{The progress bar.}
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

@@

More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies. We doubted that users would have an understanding of how the Internet well enough to even explain how Tor relays, bridges, and proxies worked. Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing. The terminology of bridges and transports are also specific to Tor, and not other censorship circumvention software.

@@

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

@@

The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}). This purpose of this introduction was to clarify that the main task
was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
We instructed them to visit a blocked and unblocked website
in a non-Tor browser to clarify that the Internet was functioning as expected. 
We then told them to use Tor Browser to visit a censored site and pointed out 
the respective shortcut on their desktop.

@@

In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges. 
Observations in E1:

@@

%P12 (regular): E2 (10:40; 0:46 to 11:26)
\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly. They then looked at proxy settings, gave up, and tried connecting directly again. Then, they tried to configure a proxy, and gave up. They tried a direct connection again, which worked unexpectedly. They found a bug in our setup that we fixed for the later experiment. E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays. }

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
	\label{fig:new-first}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
	\label{fig:new-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
	\caption{There is only one bridge screen now. The default is to connect without one.}
	\label{fig:new-nobridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
	\label{fig:new-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
	\caption{The transports selections are the same.}
	\label{fig:new-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
	\caption{These instructions are also the same.}
	\label{fig:new-bridge-help}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
	\label{fig:new-summary}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.35\textwidth}
	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
	\label{fig:new-progress}
\end{subfigure}
\caption{
A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:new-interface}
\end{figure*}

@@

\noindent To minimize work: 
\begin{itemize}
\item We eliminated technical questions, resulting in fewer tasks and interface screens. 
\item We simulated auto-detection for proxies, telling users that they did not need a proxy. This is feasible to do with a local scan (no information leaked). 
\item We labeled the configure button as an option for users in heavily censored environments.
\item We gave advice on choosing transports, telling users to try a meek bridge if obfs3 does not work.
\end{itemize}

@@

Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and started the video recording. In contrast to the previous test, we installed an instrumented version of Tor Browser 5.0.3. The instrumentation logged user interactions, such as window transitions, mouse clicks, and menu selections. Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a browser of their choice and VLC to record the screen during the experiment. Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.

@@

\begin{table}[t]
\centering
\begin{tabular}{l r r r r r}
& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
& \multicolumn{2}{r}{(at 40min 8s)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
\end{tabular}
\caption{
An overview of the results of the experiment. Those who
failed to connect were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

%table
\begin{table}[t]
\centering
\input{attempts-bridge-proxy.tex}
\caption{
Network components that led to the first successful bootstrap
in each condition.
Most successful E1 participants used a direct connection,
but a few optionally used an obfs3 bridge.
All successful E2 participants used 
an obfs3 bridge (the recommended option)---none used 
flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
Most successful E3 participants
used meek bridges, disfavoring meek-azure.
One E3 participant succeeded in an unexpected way
by using an open proxy and configuring it to bypass our 
simulated environment.
}
\label{tab:attempts-bridge-proxy}
\end{table}

@@

\begin{figure}[t]
\centering
\includegraphics{time_to_success_ecdf}
\input{time_to_success_ecdf.tex}
\caption{
Cumulative success rates over time, shown continuously and at discrete times we found interesting.
Notice that the longer the time went on, participants were less likely to succeed. 
At 1.5 minutes, every E1-NEW participant had finished,
but only 58\% of E1-OLD had finished by that time.  
At 10 minutes, most participants in E2 had finished. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

%things to keep in mind
We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1, and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely until they manually cancel the connection to try again. But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.

%configuration time and version
Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$). That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance. We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.

\begin{table}[t]
\centering
\input{median_time.tex}
\caption{The median percent of time spent on each screen. 
This percentage is computed independently for each screen; that is, a participant who spent the median percent 
of time on one screen may not be the same participant who spent the median percent
of time on other screens.} 
\label{table:median_time}
\end{table}

@@

\begin{itemize}
\item {\bfseries Hide infrequent options.} Hide the proxy configuration screen and less-used transports. None of our participants connected using flashproxy, fte, fte-ipv6, or scramblesuit transport bridges. 
\item {\bfseries Give advice.} Discourage users from configuring optional components. Add a secondary recommendation for bridges (try meek if obfs3 doesn't work, use meek if you are in China) to help users in need. 
\item {\bfseries Minimize work.} Detect if users need a proxy or not. Redirect users to the relevant pages on error (i.e. redirect to the bridge screen the bridge fails).  
\item {\bfseries Provide feedback.} Tell users what to do when a specific error occurs (i.e. try the same connection again, pick another bridge, try without a proxy, etc.).  Show users their bridge and proxy settings before and during connection. Fix the progress bar so that it updates on subsequent connections.
\end{itemize}

@@

\section{Limitations}
\label{sec:limitations}
We did not study international users, or the configuration interface in languages other than English. All of our participants were from the United States and were instructed to interact with the English version of Tor Browser.

Participants in a laboratory setting may alter their behavior due to their awareness of being observed~\cite{mccarney2007hawthorne}. We are aware that our participants were likely motivated differently compared to real users. We believe that participants were likely overmotivated to connect to Tor because they were being observed and receiving a monetary reward. If true, this makes our results are a conservative estimate of the current usability problems.

@@

Our experiment did not directly test more advanced tasks. Our simulated environments did not require users to configure a proxy or to get a custom bridge. From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how much they do.

We only tested the interface on Windows machines, which were the machines available at <redacted>. %Xlab.
The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent. Additionally, we acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.

@@

\section{Conclusion} 
\label{sec:conclusion}
The Tor Launcher GUI allows most users to connect to the Tor network, provided that the user's connection does not require a proxy or a non-default bridge. User observation showed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring proxies that they did not need. User testing showed that most people take more than 10 minutes to connect to Tor if they need to use bridges.
